Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-20 paper.tex
Comment on functional form
add some commas
tmp - adding zoom figs

Quarterly time steps have less frequent but larger impulse material flows.
The larger in-flows, however, do not compensate for the larger withdrawals
because facilities do not know about incoming inventory when they resolve
their outflow for a particular time step.  This information lag effectively
requires the floating Pu inventory to be maintained at a higher level during
the shortage.  This can be clearly seen in the Figure \ref{fig:puinv} case QF plot which has a higher
standing inventory than case MF during the fuel shortage years.  The case QF Pu
inventory is unable to drop below approximately 100 tonnes, which indicates
out-flows to be roughly equal to the Pu flow into inventory each time step
during those years.  This can be confirmed by the in-flow and inventory curves
touching at those points.  Case MF Pu inventory is similarly limited at about
the 30 tonne level.  As expected, the case QF withdrawals are also three times
higher than the case MF withdrawals, exactly matching the time step duration ratio
between the two cases.

@@

@@

>>>>

Quarterly time steps have less frequent but larger impulse material flows.
The larger in-flows, however, do not compensate for the larger withdrawals
because facilities do not know about incoming inventory when they resolve
their outflow for a particular time step.  This information lag effectively
requires the floating Pu inventory to be maintained at a higher level during
the shortage.  This can be clearly seen in Figures \ref{fig:puinv} and \ref{fig:puinv-compare} where case QF has a higher
standing inventory than case MF during the fuel shortage years.  The case QF Pu
inventory is unable to drop below approximately 100 tonnes, which indicates
out-flows to be roughly equal to the Pu flow into inventory each time step
during those years.  This can be confirmed by the in-flow and inventory curves
touching at those points.  Case MF Pu inventory is similarly limited at about
the 30 tonne level.  As expected, the case QF withdrawals are also three times
higher than the case MF withdrawals, exactly matching the time step duration ratio
between the two cases.

@@

\begin{figure*}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv-MI.eps}
    \caption[Separated Pu inventory and flow: Case MI Zoom]{
        TODO
    }
    \label{fig:puinv-MI}
\end{figure*}

\begin{figure*}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv-MF.eps}
    \caption[Separated Pu inventory and flow: Case MF Zoom]{
        TODO
    }
    \label{fig:puinv-MF}
\end{figure*}

@@

\begin{figure*}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv-compare-zoom.eps}
    \caption{
        TODO
    }
    \label{fig:puinv-compare-zoom}
\end{figure*}
